### 2023-06-12 Article.Rmd
Moderation effect interpretation

Finally, a linear regression model was fitted using `r est.n` cases from the purified dataset, values on engagement rate over .000929525 were removed because of extreme outliers and the normality of dependent variable was not met (Anderson-Darling test =`r ad.stat`, p `r ad.p`).

@@

>>>>

A linear regression model was fitted using `r est.n` cases from the purified dataset, values on engagement rate over .000929525 were removed because of extreme outliers and the normality of dependent variable was not met (Anderson-Darling test =`r ad.stat`, p `r ad.p`).

@@

Finally, the hypothesis *H~3~*: *The effect of emotional resonance on public engagement is moderated by the social media platform utilized* was also plausible (F(`r m3.F.df1`, `r m3.F.df2`)=`r m3.F`, p `r m3.F.p`), the model with interaction terms explaining `r m3.r2.p`% of engagement rate's variance (R^2^=`r m3.r2`, RSR=`r m3.RSE`) and had a statistically significant better prediction power than the second model (F(`r mod.com.df1`, `r mod.com.df2`)=`r mod.com.F`, p `r mod.com.p`).

The main effect of negative emotional resonance was statistically significant *(B=`r m3.neg.B`, t=`r m3.neg.t`, p  `r m3.neg.p`, \(\beta\)=`r m3.neg.Bt`)*, but not the main effect of positive emotional resonance *(B=`r m3.poz.B`, t=`r m3.poz.t`, p  `r m3.poz.p`, \(\beta\)=`r m3.poz.Bt`)*, and both were moderated by social network. Furthermore, compared to Twitter influence, Facebook *(B=`r m3.Fbk.B`, t=`r m3.Fbk.t`, p  `r m3.Fbk.p`, \(\beta\)=`r m3.Fbk.Bt`)* and Youtube *(B=`r m3.Yut.B`, t=`r m3.Yut.t`, p  `r m3.Yut.p`, \(\beta\)=`r m3.Yut.Bt`)* were statistically significant positively associated with engagement rate, but not Instragram *(B=`r m3.Ins.B`, t=`r m3.Ins.t`, p  `r m3.Ins.p`, \(\beta\)=`r m3.Ins.Bt`)*.

```{r, moderation-1, out.width = '510px', fig.align='center', fig.cap='Interaction effect between social network and negative emotional resonance on engagement rate', warning=FALSE}
  Int.Plot.1
```

The positive association between negative emotional resonance and engagement rate *(B=`r m3.neg.B`, t=`r m3.neg.t`, p  `r m3.neg.p`, \(\beta\)=`r m3.neg.Bt`)* was moderated statistically significant and negatively by Youtube *(B=`r m3.NegYut.B`, t=`r m3.NegYut.t`, p  `r m3.NegYut.p`, \(\beta\)=`r m3.NegYut.Bt`)* and Facebook *(B=`r m3.NegFbk.B`, t=`r m3.NegFbk.t`, p  `r m3.NegFbk.p`, \(\beta\)=`r m3.NegFbk.Bt`)*, messages with negative emotional resonance posted on these social platforms reducing statistically significant the initial positive association. No moderation effect of Instagram was identified on association between negative emotional resonance and engagement rate *(B=`r m3.NegIns.B`, t=`r m3.NegIns.t`, p  `r m3.NegIns.p`, \(\beta\)=`r m3.NegIns.Bt`)* (see Fig. \@ref(fig:moderation-1))

\center _Please Insert Fig. \@ref(fig:moderation-1) around here_ \justify

```{r, moderation-2, out.width = '510px', fig.align='center', fig.cap='Interaction effect between social network and positive emotional resonance on engagement rate', warning=FALSE}
  Int.Plot.2
```

Between positive emotional resonance and engagement rate was no statistically significant association, *(B=`r m3.poz.B`, t=`r m3.poz.t`, p  `r m3.poz.p`, \(\beta\)=`r m3.poz.Bt`)*, but our results showed a positive and statistically significant interaction effect with Instagram *(B=`r m3.PozIns.B`, t=`r m3.PozIns.t`, p  `r m3.PozIns.p`, \(\beta\)=`r m3.PozIns.Bt`)* and Youtube *(B=`r m3.PozYut.B`, t=`r m3.PozYut.t`, p  `r m3.PozYut.p`, \(\beta\)=`r m3.PozYut.Bt`)* (see Fig. \@ref(fig:moderation-2))

\center _Please Insert Fig. \@ref(fig:moderation-2) around here_ \justify

Compared to Twetter posts, if the messages with positive emotional resonance were posted on Instagram or Youtube, the engagement rate increased statistically significant and the effect was most powerfull on Instagram than on Youtube. No interaction effect was observed on Facebook related on positive emotional resonance *(B=`r m3.PozFbk.B`, t=`r m3.PozFbk.t`, p  `r m3.PozFbk.p`, \(\beta\)=`r m3.PozFbk.Bt`)*
